---
title: "Cleaning Data"
author: "Hope Kudo"
date: "12/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(tidyverse)
library(ggplot2)
library(atus)
library(shinythemes)
library(skimr)
library(readxl)
library(janitor)
library(dplyr)
library(rstanarm)
library(gtsummary) 
library(broom.mixed)
library(gt)
library(ggridges)
```

```{r}
cps <- atuscps
time <- atusact
resp <- atusresp

#join cpc and resp files together by respondent's ID number

table <- left_join(cps, resp, by = c("tucaseid")) %>% 
select(tucaseid, region, state, sex, age, edu, diary_mo, diary_day, race, famincome, tuyear, occup_code, labor_status, student_status,hh_size) %>%
  filter(tuyear == c("2012", "2013", "2014", "2015", "2016")) %>%
  distinct()

```

```{r}
#Add variables as columns to dataframe
#Sleep
sleep <- time %>%
  ungroup() %>% 
  filter(tiercode == 10101)

a <- left_join(table, sleep, by = c("tucaseid")) %>%
  mutate(sleep = dur) 
a = subset(a, select = -c(tiercode, dur)) 

#Housework
housework <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 20101, 20199))

b <- left_join(a, housework, by = c("tucaseid")) %>%
  mutate(housework = dur) 
b = subset(b, select = -c(tiercode, dur)) 

#Telephone
phonetime <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 160101, 169989))

c <- left_join(b, phonetime, by = c("tucaseid")) %>%
  mutate(phonetime = dur) 
c = subset(c, select = -c(tiercode, dur))

#Volunteer
volunteer <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 150101, 159989))

d <- left_join(c, volunteer, by = c("tucaseid")) %>%
    mutate(volunteer = dur) 
d = subset(d, select = -c(tiercode, dur))

#Playing Sports
sports <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 130101, 130199))

e <- left_join(d, sports, by = c("tucaseid")) %>%
      mutate(sports = dur) 
e = subset(e, select = -c(tiercode, dur))

#Religious Activities
religion <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 140101, 149999))

f <- left_join(e, religion, by = c("tucaseid")) %>%
      mutate(religion = dur) 
f = subset(f, select = -c(tiercode, dur))

#Eating Meals
eating <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 110101, 119999))

g <- left_join(f, eating, by = c("tucaseid")) %>%
        mutate(eating = dur) 
g = subset(g, select = -c(tiercode, dur))

#Shopping
shopping <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 70101, 70199))

h <- left_join(g, shopping, by = c("tucaseid")) %>%
          mutate(shopping = dur) 
h = subset(h, select = -c(tiercode, dur))

#Research and Homework
research_homework <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 60301, 60399))

i <- left_join(h, research_homework, by = c("tucaseid")) %>%
            mutate(research_homework = dur) 
i = subset(i, select = -c(tiercode, dur))

#Classtime
class <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 60101, 60199))

j <- left_join(i, class, by = c("tucaseid")) %>%
              mutate(class = dur) 
j = subset(j, select = -c(tiercode, dur))

#Working 
working <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 50101, 59999))

k <- left_join(j, working, by = c("tucaseid")) %>%
              mutate(working = dur) 
k = subset(k, select = -c(tiercode, dur))

#Socializing
socialevents <- time %>%
  ungroup() %>% 
  filter(between(tiercode, 120201, 120299 | 129999))

l <- left_join(k, socialevents, by = c("tucaseid")) %>%
                mutate(socialevents = dur) 
l = subset(l, select = -c(tiercode, dur))

#Television
tv <- time %>%
  ungroup() %>%
  filter(between(tiercode, 120303, 120304))

m <- left_join(l, tv, by = c("tucaseid")) %>%
                mutate(tv = dur) 
m = subset(m, select = -c(tiercode, dur))

#Drug Use
druguse <- time %>%
  ungroup() %>% 
  filter(tiercode == 120302)

n <- left_join(m, tv, by = c("tucaseid")) %>%
                mutate(druguse = dur) 
n = subset(n, select = -c(tiercode, dur))

#Computer Usage
computeruse <- time %>%
  ungroup() %>% 
  filter(tiercode == 120308)

o <- left_join(n, computeruse, by = c("tucaseid")) %>%
                mutate(computeruse = dur) 
o = subset(o, select = -c(tiercode, dur))

#Get rid of duplicate rows
data <- o %>%
  distinct() 
data <- data[!duplicated(data$tucaseid), ]

#Change N/A variables to value of 0
data$sleep[which(is.na(data$sleep))] <- 0
data$housework[which(is.na(data$housework))] <- 0 
data$phonetime[which(is.na(data$phonetime))] <- 0 
data$volunteer[which(is.na(data$volunteer))] <- 0 
data$sports[which(is.na(data$sports))] <- 0 
data$religion[which(is.na(data$religion))] <- 0 
data$eating[which(is.na(data$eating))] <- 0 
data$shopping[which(is.na(data$shopping))] <- 0 
data$research_homework[which(is.na(data$research_homework))] <- 0 
data$class[which(is.na(data$class))] <- 0 
data$working[which(is.na(data$working))] <- 0 
data$tv[which(is.na(data$tv))] <- 0 
data$computeruse[which(is.na(data$computeruse))] <- 0 
data$druguse[which(is.na(data$druguse))] <- 0 

#Change min to hours
data$sleep <- data$sleep / 60
data$housework <- data$housework / 60
data$phonetime <- data$phonetime / 60
data$volunteer <- data$volunteer / 60
data$sports <- data$sports / 60
data$religion <- data$religion / 60
data$eating <- data$eating / 60
data$shopping <- data$shopping / 60
data$research_homework <- data$research_homework / 60
data$class <- data$class / 60
data$working <- data$working / 60
data$tv <- data$tv / 60
data$computeruse <- data$computeruse / 60
data$druguse <- data$druguse / 60

```

```{r}
model1 <- lm(data = data, 
         eating ~ age + sex + race + famincome)
summary(model1)
```


```{r}
hawaii <- data %>%
  filter(state == "HI") 

fit_obj <- stan_glm(data = hawaii,
                    formula = sleep,
                    refresh = 0)

fit_obj %>%
  tbl_regression() %>%
  as_gt()

fit_obj_posterior <- posterior_predict(fit_obj, newdata = hawaii) %>%
  as_tibble() %>% 
  mutate_all(as.numeric)

fit_obj_posterior %>%

  ggplot(aes(x = hours)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
    alpha = 0.5, 
                 bins = 90, 
                 position = "identity")

```

```{r}
# Sleep

sleep1 <- data %>%
  select(state, sleep, housework, phonetime, volunteer, sports, religion, 
         eating, shopping, research_homework, class, working, tv, druguse,
         computeruse) %>%
  group_by(state) %>%
  summarise(mean(sleep)) 

# Housework

housework1 <- data %>%
  select(state, housework) %>%
  group_by(state) %>%
  summarise(mean(housework))

combo1 <- left_join(sleep1, housework1, by = c("state"))

# Phonetime

phonetime1 <- data %>%
  select(state, phonetime) %>%
  group_by(state) %>%
  summarise(mean(phonetime))

combo2 <- left_join(combo1, phonetime1, by = c("state"))

# Volunteering

volunteer1 <- data %>%
  select(state, volunteer) %>%
  group_by(state) %>%
  summarise(mean(volunteer))

combo3 <- left_join(combo2, volunteer1, by = c("state"))

# Sports

sports1 <- data %>%
  select(state, sports) %>%
  group_by(state) %>%
  summarise(mean(sports))

combo4 <- left_join(combo3, sports1, by = c("state"))

# Religion

religion1 <- data %>%
  select(state, religion) %>%
  group_by(state) %>%
  summarise(mean(religion))

combo5 <- left_join(combo4, religion1, by = c("state"))

# Eating

eating1 <- data %>%
  select(state, eating) %>%
  group_by(state) %>%
  summarise(mean(eating))

combo6 <- left_join(combo5, eating1, by = c("state"))

# Shopping

shopping1 <- data %>%
  select(state, shopping) %>%
  group_by(state) %>%
  summarise(mean(shopping))

combo7 <- left_join(combo6, shopping1, by = c("state"))

# Research and Homework
researchhomework1 <- data %>%
  select(state, research_homework) %>%
  group_by(state) %>%
  summarise(mean(research_homework))

combo8 <- left_join(combo7, researchhomework1, by = c("state"))

# Class

class1 <- data %>%
  select(state, class) %>%
  group_by(state) %>%
  summarise(mean(class))

combo9 <- left_join(combo8, class1, by = c("state"))

# Working

working1 <- data %>%
  select(state, working) %>%
  group_by(state) %>%
  summarise(mean(working))

combo10 <- left_join(combo9, working1, by = c("state"))

# Television Use

tv1 <- data %>%
  select(state, tv) %>%
  group_by(state) %>%
  summarise(mean(tv))

combo11 <- left_join(combo10, tv1, by = c("state"))

# Drug Use

druguse1 <- data %>%
  select(state, druguse) %>%
  group_by(state) %>%
  summarise(mean(druguse))

combo12 <- left_join(combo11, druguse1, by = c("state"))

# Computer Use

computeruse1 <- data %>%
  select(state, computeruse) %>%
  group_by(state) %>%
  summarise(mean(computeruse)) 

combo13 <- left_join(combo12, computeruse1, by = c("state")) %>%
    mutate("Avg Comp. Use" = mean(computeruse))

combo13%>%
  ungroup() 

combo13
```
# Create a distribution, x = hours, y = frequency. Create a normal histogram for each state
# Compare states, display two plots on the page, create two different plots and set a default. Alphabetical set. Have them be automatically populated. Have two separate dropdowns. 

# Need a statistical regression, y = hours

```{r}
model <- lm(data = data, 
         sleep ~ state + age + sex + race)

summary(model)

# Make a distribution for each state, refer to exam 3, x = estimates, y = variables (states, race, income)
# add a table and describe what its doing, find format from the textbook. 
```
#*** = prob of getting a result this extreme given null hypotheis that sex is equal is extremely unlikely, thus, we would trust the values generated


```{r}
set.seed(15)
fit_obj <- stan_glm(data = data,
                    formula = sleep ~ race,
                    refresh = 0)
#print(fit_obj, view = FALSE, digits = 5)

fit_obj %>%
  tbl_regression() %>%
  as_gt() 

fit_obj
```


```{r}

model3 <- lm(data = data, 
         working ~ age + sex + race + famincome)
summary(model3)

```

#shiny app code
obj <- "housework"
data %>%
  ggplot(aes(x = obj)) +
  geom_density()


```{r}
write.csv(data, "projects/americantimeanalysis/fullset.csv")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.